systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-16 paper/trunk/systemfit_other.tex
revised paragraph about the WSUR and W3SLS method and paragraph about iterated WLS/SUR/W2SLS/3SLS
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@601 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The WLS, SUR, W2SLS and 3SLS parameter estimates are consistent,
if the estimated residual variance-covariance matrix is calculated
using the residuals from a first-step OLS or 2SLS estimation.
The software LIMDEP calculates SUR or 3SLS estimates by a
slightly different approach.
It uses the residuals of a first-step OLS or 2SLS estimation
for a second-step WLS or W2SLS estimation,
and then calculates the residual variance covariance matrix
from the residuals of the WLS or W2SLS estimation
to estimates the model by SUR or 3SLS in a third step
\citep{greene06}.
It is also possible to iterate the estimation procedure and
calculate the residual variance-covariance matrix from the
residuals of the previous iteration. 
If equation (\ref{eq:rcov0}) is applied to calculate the estimated
residual variance-covariance matrix, the results converge to maximum
likelihood \citep[p.\ 345]{greene03}.

>>>>

The WLS, SUR, W2SLS and 3SLS parameter estimates are consistent,
if the estimated residual variance-covariance matrix is calculated
using the residuals from a first-step OLS or 2SLS estimation.
There exists also an alternative slightly different approach.%
\footnote{
For instance, this approach is applied by
the command °TSCS° of the software LIMDEP that carries out SUR estimations
in which all coefficient vectors are constrained to be equal
\citep{greene06}.
}
It uses the residuals of a first-step OLS or 2SLS estimation
to apply a WLS or W2SLS estimation on a second step.
Then, it calculates the residual variance covariance matrix
from the residuals of the second-step estimation
to estimates the model by SUR or 3SLS in a third step.
If no cross-equation restrictions are imposed,
the parameter estimates of OLS and WLS as well as 2SLS and W2SLS are identical.
Hence, in this case the both approach generate the same results.

It is also possible to iterate WLS, SUR, W2SLS and 3SLS estimations.
At each iteration the residual variance-covariance matrix is calculated
from the residuals of the previous iteration.
If equation (\ref{eq:rcov0}) is applied to calculate the estimated
residual variance-covariance matrix,
an iterated SUR estimation converges to maximum
likelihood \citep[p.\ 345]{greene03}.
